
\abstractheader
%-----------------------Begin Abstract ------------------------------
This is a sample thesis approved by the graduate office. I decided to
make it available for every student at the Case Western Reserve
University. If you use the {\bf``CWRU-THESIS.sty''} style file, you
won't have to visit the graduate office for format information. Simply
modify the sample thesis by using your own text and run it using
{\bf\LaTeX}.

The title of this document is same as the title of my dissertation;
because I want to show you how the CWRU-THESIS style file makes the
title. The committee page is optional, so you may just ignore it; the
dedication and acknowledgment are from my dissertation just to pay
tribute to those who have helped me.

In this sample document I will explain how to make the {\bf
bibliography} and {\bf index} of your thesis.

Making the index is the last step in preparing your document.
Generally, indexes (indices) are not made for dissertations or master
theses because because they are very difficult to make. I worked very
hard to learn how to make it, and therefore I have included the index
in my dissertation and am leaving it to your discretion as to whether
to add an index to your document.

If you have any question or problem with \LaTeX try accessing the
Internet news group {\bf comp.text.tex}; I got a lot of help there. If
you have access to me, you are very welcome to ask me, or you may ask
for help from a \LaTeX hacker near you.
%-----------------------End Abstract --------------------------------
