\newpage
\begin{center}
{\Large \bf ACKNOWLEDGEMENTS}
\end{center}

\vspace*{0.2in}
I feel pleasure to acknowledge those who have helped me in every
aspect of my life and educational career.

First, I acknowledge all my teachers from grade one to Ph.D.,
including my father, who was a primary school teacher and taught me in
grades four and five.

I am very thankful to {\bf Dr. Christos A. Papachristou} for accepting
me as an advisee in my Ph.D. program, and for his tolerance and
guidance through some of my stupid questions. I also appreciate his
help in solving my personal problems. I consider him a mentor whose
name will always remain with me as long as I am alive. I am very lucky
and proud to have him as my advisor.

My gratitude for {\bf Dr. Raymond A. Neff}, Vice President, CWRU, {\bf
Mr. James A. Barker}, Director IBM/CWRU Electronic Library Project,
and {\bf Ms.  Lizann A. Slotta}, my supervisor, for hiring me on the
Electronic Library Project, and supporting me so that I could earn a
living and make this day happen. I must also thank {\bf Dr. Lee J.
White}, chairman of our department, for recommending and providing me
with research assistantship through the Electronic Library Project.

I would like to thank {\bf Dr. George Ernst}, {\bf Dr. Frank Merat},
{\bf Dr. Sheldon Gruber}, and {\bf Dr. Yoshiyasu Takefuji} for being
on my dissertation committee. I am also thankful to {\bf Dr. Saad
Harous} who was on my Ph.D. proposal committee, then got a faculty
position in Oman and could not stay until my dissertation defense.

I appreciate the cooperation of my wife {\bf Nargis}, who joined me on
December 29, 1990, in the third year of my Ph.D. program for her
encouragement, my sons {\bf Qasim}, born on Sept. 11, 1991, and {\bf
Ahmed}, born on February 23, 1993, for being patient with me for not
taking them for a ride everyday when I was busy with my job and
school.

I deeply acknowledge the guardianship and moral support of my brother
{\bf Mr. Hadi Bux Soomro} who has always been with me like my father
at every stage of my life. I must acknowledge the cooperation and help
of my younger brother {\bf Dr. Abdul Rahim Soomro} who always shared
his financial assistance during his school years at Chandka and Sindh
Medical Colleges, with me during my under graduate years at Mehran
University of Engineering \& Technology.

I am very grateful to {\bf Dr. Ali N. Shaikh, M.D.}, for his financial
support during my jobless period at Case Western Reserve University. I
would also like to thank {\bf Dr. Nandlal Varyani, M.D.}, for hiring
me at The Surgery Center during my bad days. I do appreciate and
remember all of those who financially and morally supported me during
my undergraduate studies at Mehran University of Engineering \&
Technology, especially {\bf Begum Khadija Khanum Daudpoto} and {\bf
Dr. Isa Daudpoto}.

I would like to thank the members of the SYNTEST group: {\bf Joan
Carletta, Wen-Chen Chen, Scott Chiu, Haidar Harmanani, Mehrad Nourani,
and Ricardo Schaffner}. They have made my study at Case Western
Reserve University a pleasant memory; they always helped me when I was
in need. I am so grateful to {\bf Venkatesh Srinivasan}, {\bf Ashish
Jain}, the emacs guru, and {\bf Amit Kohli} for helping me in each
aspect of the course. Without their assistance it would have been
difficult for me to find programming shortcuts in the {\bf C}
language. I thank all the faculty, staff, and secretaries in the
department of computer engineering \& science from Fall 1988 'till
Fall 1993 for their help and assistance.

Finally, I do appreciate {\bf Mrs. Leah Shaikh} who proofread my Ph.D.
research proposal in one shot until 2 o'clock in the morning, and {\bf
Mr. Tom Roberts} for proofreading my dissertation.
